### 2018-08-08 paper/evaluation.tex
up

In the following, we first give precisions on the evaluation testbed and parameters in section~\ref{sub:evaluation_testbed}, before evaluating the PORs creation in section~\ref{sub:predictive_onion_routes_creation}, to conclude with an overall evaluation of the file transfer performance in section~\ref{sub:file_transfer}.

>>>>

In the following, we first give precisions on the evaluation testbed and parameters in section~\ref{sub:evaluation_testbed}, before evaluating the file transfer performance in section~\ref{sub:file_transfer}.
